Ellicular galaxies and their (non over-massive) black holes

### 2015-10-01 papers/ellicular/ellicular.tex
holidays

\documentclass[useAMS,usenatbib,article]{mn2e}

\usepackage{longtable}
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{natbib}
\bibliographystyle{mn2e}
%\usepackage{tabularx}
%\usepackage{bm}
%\usepackage{color}
%\usepackage{hyperref}

%% Sometimes a paper's abstract is too long to fit on the
%% title page in preprint2 mode. When that is the case,
%% use the longabstract style option.

%% \documentclass[preprint2,longabstract]{aastex}
\newcommand\aj{{AJ}}%
\newcommand\actaa{{Acta Astron.}}%
\newcommand\araa{{ARA\&A}}%
\newcommand\apj{{ApJ}}%
\newcommand\apjl{{ApJ}}%
\newcommand\apjs{{ApJS}}%
\newcommand\ao{{Appl.~Opt.}}%
\newcommand\apss{{Ap\&SS}}%
\newcommand\aap{{A\&A}}%
\newcommand\aapr{{A\&A~Rev.}}%
\newcommand\aaps{{A\&AS}}%
\newcommand\azh{{AZh}}%
\newcommand\baas{{BAAS}}%
\newcommand\caa{{Chinese Astron. Astrophys.}}%
\newcommand\cjaa{{Chinese J. Astron. Astrophys.}}%
\newcommand\icarus{{Icarus}}%
\newcommand\jcap{{J. Cosmology Astropart. Phys.}}%
\newcommand\jrasc{{JRASC}}%
\newcommand\memras{{MmRAS}}%
\newcommand\mnras{{MNRAS}}%
\newcommand\na{{New A}}%
\newcommand\nar{{New A Rev.}}%
\newcommand\pra{{Phys.~Rev.~A}}%
\newcommand\prb{{Phys.~Rev.~B}}%
\newcommand\prc{{Phys.~Rev.~C}}%
\newcommand\prd{{Phys.~Rev.~D}}%
\newcommand\pre{{Phys.~Rev.~E}}%
\newcommand\prl{{Phys.~Rev.~Lett.}}%
\newcommand\pasa{{PASA}}%
\newcommand\pasp{{PASP}}%
\newcommand\pasj{{PASJ}}%
\newcommand\qjras{{QJRAS}}%
\newcommand\rmxaa{{Rev. Mexicana Astron. Astrofis.}}%
\newcommand\skytel{{S\&T}}%
\newcommand\solphys{{Sol.~Phys.}}%
\newcommand\sovast{{Soviet~Ast.}}%
\newcommand\ssr{{Space~Sci.~Rev.}}%
\newcommand\zap{{ZAp}}%
\newcommand\nat{{Nature}}%
\newcommand\iaucirc{{IAU~Circ.}}%
\newcommand\aplett{{Astrophys.~Lett.}}%
\newcommand\apspr{{Astrophys.~Space~Phys.~Res.}}%
\newcommand\bain{{Bull.~Astron.~Inst.~Netherlands}}%
\newcommand\fcp{{Fund.~Cosmic~Phys.}}%
\newcommand\gca{{Geochim.~Cosmochim.~Acta}}%
\newcommand\grl{{Geophys.~Res.~Lett.}}%
\newcommand\jcp{{J.~Chem.~Phys.}}%
\newcommand\jgr{{J.~Geophys.~Res.}}%
\newcommand\jqsrt{{J.~Quant.~Spec.~Radiat.~Transf.}}%
\newcommand\memsai{{Mem.~Soc.~Astron.~Italiana}}%
\newcommand\nphysa{{Nucl.~Phys.~A}}%
\newcommand\physrep{{Phys.~Rep.}}%
\newcommand\physscr{{Phys.~Scr}}%
\newcommand\planss{{Planet.~Space~Sci.}}%
\newcommand\procspie{{Proc.~SPIE}}%

%\newcommand{\vdag}{(v)^\dagger}
%\newcommand{\myemail}{gsavorgn@astro.swin.edu.au}
%\newcommand{\fitfigurewidth}{0.8\textwidth}

%\title[Intermediate-scale discs]{Early-type galaxies with intermediate-scale discs and their ordinary supermassive black holes}
\title[Ellicular galaxies]{Ellicular galaxies and their (non over-massive) black holes}

@@

\begin{abstract}
The classification ``early-type'' galaxy includes both elliptically- and lenticular-shaped galaxies, 
with the latter composed of a spheroidal stellar system encased within a larger, but flatter, stellar disc. 
Theoretically, the spheroid-to-disc flux ratio can assume any positive value,  
but in practice studies often consider only spheroid/disc decompositions 
in which the disc neatly dominates over the spheroid at large galaxy radii, 
creating an inner ``bulge'' as observed in most spiral galaxies. 
Here we reveal that decompositions in which the disc remains embedded within the spheroid, labelled by some as ``unphysical'',  
correctly reproduce both the photometric and kinematic properties of a class of early-type galaxy 
intermediate between that of elliptical and lenticular galaxies, which we refer to as \emph{ellicular} galaxies for ease of reference. 
Ellicular galaxies have often been confused with lenticular galaxies, 
such that %their disc luminosities have been considerably overestimated 
their spheroid luminosities have been considerably underestimated. 
This has recently led to some surprising conclusions, 
such as the claim that a number of ellicular galaxies (e.g.~Mrk 1216, NGC 1277, NGC 1271, and NGC 1332) 
host a central black hole whose mass is abnormally large compared to expectations from the (underestimated) spheroid luminosity. 
We show that when ellicular galaxies are correctly modeled, 
they no longer appear as extreme outliers in the (black hole mass)-(spheroid mass) diagram. 
This not only nullifies the need for invoking different evolutionary scenarios for these galaxies 
but it strengthens the significance of the observed (black hole mass)-(spheroid mass) correlation 
and confirms its importance as a fundamental ingredient for theoretical and semi-analytic models 
used to describe the coevolution of spheroids and their central supermassive black holes.

@@

\begin{keywords}
black hole physics -- galaxies: bulges -- galaxies: elliptical and lenticular, cD -- galaxies: evolution -- galaxies: structure
\end{keywords}

@@

The first are the large-scale discs (with sizes of a few kiloparsec) 

@@

(e.g.~\citealt{whiterees1978,whitefrenk1991,navarrobenz1991,khochfarsilk2006,dekel2009nat,ceverino2010,ceverino2012,conselice2012}), 

@@

Here we report on the photometric and kinematical signatures of these intermediate-sized stellar discs 
and the impact this has on the (black hole mass)-to-(spheroid stellar mass) ratio %, $M_{\rm BH}/M_{*,sph}$, 

@@

%A puzzling question, which has been unspoken for decades, is why are there not intermediate-sized discs: 
%why are there not accretion events which create discs larger than the typical nuclear discs but which are not large enough to dominate at large radii? 

@@

Most early-type galaxies are classified as ``central fast rotators'' \citep{atlas3dIII-MNRAS}, 

@@

A specific angular momentum profile that is rapidly increasing beyond $1-2$ half-light radii 

@@

while a specific angular momentum profile that increases up to $1-2$ half-light radii and then declines beyond that point 

@@

The toy model shown in Figure \ref{fig:model} illustrates the typical ellipticity profile 

@@

(i) a lenticular galaxy comprised of a large-scale disc and a relatively smaller encased bulge, 
(ii) an elliptical galaxy with a nuclear stellar disc, 
and (iii) a galaxy composed of an intermediate-scale disc embedded in a relatively larger spheroid. 
We refer to the last case as an ellicular galaxy. 

@@

whereas a radial decrease of ellipticity signifies the opposite case. \\

@@

dates back at least three decades 
\citep{capaccioli1987,carter1987,rixwhite1990,bender1990,scorzabender1990,nieto1991,rixwhite1992,scorzabender1995,
donofrio1995,graham1998fornax,scorza1998,scorzavandenbosch1998} and, 

@@

However, the class of ellicular galaxies has been missed by many galaxy modellers, 

@@

This bias has led to the rejection of many spheroid/disc decompositions similar to that illustrated in the middle panel of Figure \ref{fig:model}. 

@@

(e.g.~\citealt{gadotti2008,head2014,querejeta2015,mendezabreu2015}). \\
{\bf This paper is structured as follows. 

@@

and we briefly describe other five ellicular galaxies (NGC 821, NGC 1271, NGC 1277, NGC 3377, and NGC 4697). 
We compare our photometric analysis with the kinematical information available from the literature 

@@

and we update the Hubble grid with the inclusion of ellicular galaxies. }

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{images/discmodel.eps}
\caption{Illustration of the spheroid/disc decomposition of the one-dimensional surface brightness profile, $\mu$, 
the ellipticity profile, $\epsilon$, and the specific angular momentum profile, $\lambda$,
for the three prototype early-type galaxy sub-classes. 
In the flux decompositions, the spheroid (or bulge) and the disc are shown with the red and blue color, respectively. 
The left panel shows a lenticular galaxy, composed of a bulge encased in a large-scale disc. 
The right panel displays an elliptical galaxy with (an optional) nuclear stellar disc. 
The middle panel presents an early-type galaxy with an intermediate-sized disc embedded in the spheroid. 
We refer to the last case as an ellicular galaxy.}
\label{fig:model}
\end{center}
\end{figure}

@@

\subsection{NGC 3115}
The presence of a disc in NGC 3115 is obvious due to its edge-on orientation (Figure \ref{fig:n3115}). 
Less obvious is the radial extent of this disc, if one only relies on a visual inspection of the galaxy image. 
The ellipticity profile (Figure \ref{fig:n3115}) is consistent with the presence of an intermediate-scale disc. 
Moreover, the kinematics of NGC 3115 \citep{arnold2011n3115} also disprove the presence of a large-scale disc, 
because the galaxy is rapidly rotating only within two galaxy half-light radii ($\sim 2 \times 50~\rm arcsec$), 
and the rotation significantly drops at larger radii.  
The unsharp mask of NGC 3115 (Figure \ref{fig:n3115}) betrays the presence of a faint edge-on nuclear ring, 
which can also be spotted as a small peak in the ellipticity profile 
(at semimajor-axis length $R_{\rm maj} \sim 15~\rm arcsec$).
The spheroidal component of NGC 3115 is well described with a \cite{sersic1963} profile.
The highly inclined intermediate-scale disc is better fit with an $n<1$ S\'ersic profile 
(the S\'ersic index $n$ regulates the curvature of the S\'ersic profile) 
rather than with an exponential function, 
as explained by \cite{pastrav2013a}. 
The nuclear ring is modelled with a Gaussian function. \\
In comparison, \cite{lasker2014data} fit NGC 3115 with a bulge + disc + envelope, 
and measured a bulge half-light radius of $3.9~\rm arcsec$ and a bulge-to-total ratio of $0.12$. 
We describe this galaxy using a spheroid + intermediate-scale disc + nuclear ring, 
and obtain a spheroid half-light radius of $43.6~\rm arcsec$ and a spheroid-to-total ratio of $0.85$. 
We have used both kinematical information and ellipticity profiles, 
together with the surface brightness profile, 
to obtain a physically consistent and meaningful model.

\subsection{NGC 1332}
The morphology of NGC 1332 (Figure \ref{fig:n1332}) is very similar to that of NGC 3115, 
with the ellipticity profile indicating the presence of an intermediate-scale disc, 
although in this case no nuclear component is evident. 
We were not able to find any extended kinematic profile or map 
for this galaxy in the literature. 
The data within the innermost $6~\rm arcsec$ were excluded from the fit 
because, according to our galaxy decomposition, they are possibly affected by the presence of a partially depleted core.
The surface brightness profile of NGC 1332 is well described with a S\'ersic-spheroid plus
an $n<1$ S\'ersic-disc. 
Our galaxy decomposition suggests that NGC 1332 is a spheroid-dominated galaxy, 
with a spheroid-to-total ratio of $0.95$. \\
\cite{rusli2011} did not identify the restricted extent of the intermediate-scale disc, 
as revealed by the ellipticity profile, 
and proposed a model featuring a S\'ersic-bulge and a large-scale exponential-disc, 
with a spheroid-to-total ratio of $0.43$.
Based on their bulge/disc decomposition, they concluded that NGC 1332 is a disc dominated lenticular galaxy 
which is displaced from the (black hole mass)-(spheroid luminosity) correlation of \cite{marconihunt2003} 
by an order of magnitude along the black hole mass direction. 
However, in Section \ref{sec:mm} we show that, according to our decomposition, 
NGC 1332 lies within the $1\sigma$ scatter about the (black hole mass)-(spheroid stellar mass) correlation 
for early-type galaxies. 
{\bf We also note that the majority of galaxies with an elevated stellar velocity dispersion ($\sigma > 270~\rm km~s^{-1}$) 
are core-S\'ersic galaxies \citep{graham2003coresersicmodel,trujillo2004coresersicmodel,dullograham2014cores}, 
i.e.~they have a partially depleted core which has been identified from high-resolution photometric data. 
NGC 1332 has $\sigma = 320~\rm km~s^{-1}$, but, 
based on their decomposition of \emph{HST} imaging, \cite{rusli2011} did not find a core in this galaxy. 
However, the identification of a partially depleted core is model dependent, 
that is, only a correct galaxy decomposition can confirm or rule out the presence of a core. 
Our galaxy decomposition (Figure \ref{fig:n1332}) suggests that NGC 1332 is in fact a core-S\'ersic galaxy. 
Since we did not use high-resolution photometric data, 
we refrain from a firm conclusion, 
but we caution that a re-analysis of the \emph{HST} data -- by taking into account the correct radial extent of the intermediate-scale disc --
may indeed reveal the presence of a core.}

@@

\subsubsection{NGC 1271}
{\bf \cite{walsh2015} explored a three-component decomposition for NGC 1271 
and identified the galaxy bulge with the innermost of the three components, 
having a half-light radius of $0.61~\rm arcsec$ and a bulge-to-total ratio of $0.23$; 
our model features a spheroid + intermediate-scale disc, 
with a spheroid half-light radius of $3.3~\rm arcsec$ and a spheroid-to-total ratio of $0.67$. }

\subsubsection{NGC 1277}
\cite{vandenbosch2012} proposed a model for the galaxy NGC 1277 with a bulge + disc + nuclear source + envelope, 
which gives a bulge half-light radius of $0.9~\rm arcsec$ and a bulge-to-total ratio of $0.24$; 
our model consists of a spheroid + intermediate-scale disc + nuclear component, 
and produces a spheroid half-light radius of $6.0~\rm arcsec$ and a spheroid-to-total ratio of $0.79$.

\subsubsection{NGC 3377}
\cite{lasker2014data} modelled the galaxy NGC 3377 with a bulge + nuclear disc + disc + envelope, 
and obtained a bulge half-light radius of $10.1~\rm arcsec$ and a bulge-to-total ratio of $0.35$; 
our model with a spheroid + intermediate-scale disc + nuclear disc 
returns a spheroid half-light radius of $61.8~\rm arcsec$ and a spheroid-to-total ratio of $0.94$.

\subsubsection{NGC 821}
\cite{lasker2014data} decomposed the galaxy NGC 821 into a bulge + disc + envelope, 
and measured a bulge half-light radius of $3.8~\rm arcsec$ and a bulge-to-total ratio of $0.19$; 
our decomposition consists of a spheroid + intermediate-scale disc, 
with a spheroid half-light radius of $36.5~\rm arcsec$ and a spheroid-to-total ratio of $0.79$.

\subsubsection{NGC 4697}
The galaxy NGC 4697 represents an ``extreme'' case. 
\cite{lasker2014data} fit this galaxy with a bulge + nuclear source + disc + envelope, 
and obtained a bulge half-light radius of $6.3~\rm arcsec$ and a bulge-to-total ratio of $0.08$; 
we described NGC 4697 using a spheroid + intermediate-scale disc + nuclear disc model, 
and measured a spheroid half-light radius of $239.3~\rm arcsec$ and a spheroid-to-total ratio of $0.89$. \\

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/n3115_image.jpeg}
\includegraphics[width=0.49\columnwidth]{images/n3115_unsharp.jpeg} \\
\includegraphics[width=1.05\columnwidth]{images/n3115_decomposition.pdf}
\caption{NGC 3115. 
The top panels are the \emph{Spitzer}/IRAC $3.6~\rm \mu m$ image (left) and its unsharp mask (right), 
obtained by dividing the image by a Gaussian-smoothed version of itself. 
The bottom plots display the best-fit model of the surface brightness profile, $\mu$, 
and the ellipticity profile, $\epsilon$, 
along the major-axis, $R_{\rm maj}$. 
The black points are the observed data, which extend out to five galaxy half-light radii ($\sim 5 \times 50~\rm arcsec$). 
The color lines represent the individual (PSF-convolved) model components: 
red = S\'ersic (spheroid), blue = S\'ersic (disc), gray = Gaussian ring. 
The residual profile (data $-$ model) is shown as $\Delta \mu$. 
The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations. 
$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$. }
\label{fig:n3115}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/n1332_image}
\includegraphics[width=0.49\columnwidth]{images/n1332_unsharp} \\
\includegraphics[width=1.03\columnwidth]{images/n1332_decomposition.pdf}
\caption{NGC 1332.
Same as Figure \ref{fig:n3115}, except for the following. 
The surface brightness profile extends out to seven galaxy half-light radii ($\sim 7 \times 20~\rm arcsec$). 
The empty points are data excluded from the fit. 
%The top panels are the \emph{Spitzer}/IRAC $3.6~\rm \mu m$ image (left) and its unsharp mask (right), 
%obtained by dividing the image by a Gaussian-smoothed version of itself. 
%The bottom plots display the best-fit model of the surface brightness profile, $\mu$, 
%and the ellipticity profile, $\epsilon$, 
%along the major-axis, $R_{\rm maj}$. 
%The black points are the observed data, which extend out to seven galaxy half-light radii ($\sim 7 \times 20~\rm arcsec$). 
%The empty points are data excluded from the fit.   
%The color lines represent the individual (PSF-convolved) model components: 
%red = S\'ersic (spheroid), blue = S\'ersic (disc). 
%The residual profile (data $-$ model) is shown as $\Delta \mu$. 
%The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations. 
%$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$.
}
\label{fig:n1332}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{images/mrk1216_image.jpeg}
\includegraphics[width=0.49\columnwidth]{images/mrk1216_unsharp.jpeg} \\
\includegraphics[width=1.05\columnwidth]{images/mrk1216_decomposition.pdf}
\caption{Mrk 1216. 
Same as Figure \ref{fig:n3115}, except for the following. 
The top panels are the \emph{HST}/WFC3 \emph{F160W} image (left) and its unsharp mask (right).
The surface brightness profile extends out to five galaxy half-light radii ($\sim 5 \times 5~\rm arcsec$). 
The color lines represent the individual (PSF-convolved) model components:
red = S\'ersic (spheroid), blue = exponential (disc).
%The top panels are the \emph{HST}/WFC3 \emph{F160W} image (left) and its unsharp mask (right),
%obtained by dividing the image by a Gaussian-smoothed version of itself.
%The bottom plots display the best-fit model of the surface brightness profile, $\mu$,
%and the ellipticity profile, $\epsilon$,
%along the major-axis, $R_{\rm maj}$.
%The black points are the observed data, which extend out to five galaxy half-light radii ($\sim 5 \times 5~\rm arcsec$).
%The color lines represent the individual (PSF-convolved) model components:
%red = S\'ersic (spheroid), blue = exponential (disc).
%The residual profile (data $-$ model) is shown as $\Delta \mu$.
%The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations.
%$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$.
}
\label{fig:m1216}
\end{center}
\end{figure}

@@

but almost constant mass-to-light ratios ($\sim$$0.6$, \citealt{meidt2014-MNRAS}). \\

@@

%The luminosity of the spheroidal component of this galaxy comes from the one-dimensional spheroid/disc decomposition 
%of Graham, Savorgnan \& Ciambur (\emph{in prep.}),  
%who used an archived \emph{HST} image taken with the WFC3 and the near-infrared \emph{F160W} filter. 

@@

%The luminosity of the spheroidal component of this galaxy comes from the one-dimensional spheroid/disc decomposition of Graham et al.~(\emph{in prep.}), 

>>>>

\documentclass[useAMS,usenatbib,article]{mnras}

\usepackage{longtable}
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{natbib}
\bibliographystyle{mnras}

\title[Ellicular galaxies]{Ellicular galaxies and their (non over-massive) black holes}

@@

\begin{abstract}
The classification ``early-type'' galaxy includes both elliptically- and lenticular-shaped galaxies, 
with the latter composed of a spheroidal stellar system encased within a larger, but flatter, stellar disc. 
Theoretically, the spheroid-to-disc flux ratio can assume any positive value,  
but in practice studies often consider only spheroid/disc decompositions 
in which the disc neatly dominates over the spheroid at large galaxy radii, 
creating an inner ``bulge'' as observed in most spiral galaxies. 
Here we reveal that decompositions in which the disc remains embedded within the spheroid, labelled by some as ``unphysical'',  
correctly reproduce both the photometric and kinematic properties of a class of early-type galaxy 
intermediate between that of elliptical and lenticular galaxies, which we refer to as \emph{ellicular} galaxies for ease of reference. 
Ellicular galaxies have often been confused with lenticular galaxies, 
such that their spheroid luminosities have been considerably underestimated. 
This has recently led to some surprising conclusions, 
such as the claim that a number of ellicular galaxies (e.g.~Mrk 1216, NGC 1277, NGC 1271, and NGC 1332) 
host a central black hole whose mass is abnormally large compared to expectations from the (underestimated) spheroid luminosity. 
We show that when ellicular galaxies are correctly modelled, 
they no longer appear as extreme outliers in the (black hole mass)-(spheroid mass) diagram. 
This not only nullifies the need for invoking different evolutionary scenarios for these galaxies 
but it strengthens the significance of the observed (black hole mass)-(spheroid mass) correlation 
and confirms its importance as a fundamental ingredient for theoretical and semi-analytic models 
used to describe the coevolution of spheroids and their central supermassive black holes.

@@

\begin{keywords}
galaxies: classification -- galaxies: bulges -- galaxies: elliptical and lenticular, 
cD -- galaxies: evolution -- galaxies: structure -- galaxies: individual: Mrk 1216, NGC 1271, NGC 1277, NGC 1332, NGC 4291
\end{keywords}

@@

The first are the large-scale discs (with exponential scale lengths of a few kiloparsec) 

@@

(e.g.~\citealt{whiterees1978,whitefrenk1991,navarrobenz1991,barneshernquist1992,khochfarsilk2006,dekel2009nat,ceverino2010,
ceverino2012,conselice2012,rubin2012,martini2013,ueda2014}), 

@@

Here we focus on the increasingly overlooked occurence of intermediate-scale discs in galaxies with directly measured black hole masses. 
We report on the photometric and kinematical signatures of these intermediate-sized stellar discs,  
and the impact they have on the (black hole mass)-to-(spheroid stellar mass) ratio 

@@

@@

Most early-type galaxies are classified as ``central fast rotators'' \citep{franx1989,atlas3dIII,scott2014}, 

@@

A specific angular momentum profile that is rapidly increasing beyond 1--2 half-light radii 

@@

while a specific angular momentum profile that increases up to 1--2 half-light radii and then declines beyond that point 

@@

Building on the investigation of \cite{rixwhite1990}, 
the toy model shown in Figure \ref{fig:model} illustrates the typical ellipticity profile 

@@

(i) a ``lenticular'' galaxy comprised of a large-scale disc which dominates the light at large radii over a relatively smaller encased bulge, 
(ii) an ``elliptical'' galaxy with an additional nuclear stellar disc, 
and (iii) a galaxy composed of an intermediate-scale disc embedded in a relatively larger spheroid 
which dominates the light at large radii. 
We refer to the last case as an ``ellicular'' galaxy. 

@@

whereas a radial decrease of ellipticity signifies the opposite case. 
This approach can be taken to the next level by inspecting the isophotes for discy structures and checking the velocity line profiles for asymmetry 
(e.g.~\citealt{scorzabender1995} and references therein; \citealt{scorza1998}). \\

@@

dates back many years 
\citep{michard1984,djorgovski1985,carter1987,capaccioli1987,capaccioli1988,franx1989,nieto1988,nieto1991,rixwhite1990,rixwhite1992,
vandenbergh1990,bender1990,scorzabender1990,scorzabender1995,
simienmichard1990,cinzanovandermarel1993,donofrio1995,graham1998fornax,scorza1998,scorzavandenbosch1998,bendersaglia1999} and, 

@@

However, the class of ellicular galaxies has been missed by many galaxy modellers of late, 

@@

Indeed, \citeauthor{graham2011} (\citeyear{graham2011}, his Figure 7) warned about such erroneous fits to spiral galaxies. 
This bias has led to the rejection of many early-type galaxy decompositions similar to that illustrated in the middle panel of Figure \ref{fig:model}. 

@@

(e.g.~\citealt{gadotti2008,head2014,querejeta2015,mendezabreu2015}). 
In this paper we investigate the influence this has had on research pertaining to supermassive black hole mass scaling relations involving the host spheroid. \\
This paper is structured as follows. 

@@

and we briefly describe another five ellicular galaxies (NGC 821, NGC 1271, NGC 1277, NGC 3377, and NGC 4697) 
already modelled by us elsewhere in the literature. 
We compare our photometric analysis with the kinematical information available from the literature, 

@@

and we present the location of ellicular galaxies, relative to other galaxies, in the Hubble grid.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{discmodel.eps}
\caption{Illustration of the spheroid/disc decomposition of the one-dimensional surface brightness profile, $\mu$, 
the ellipticity profile, $\epsilon$, and the specific angular momentum profile, $\lambda$,
for the three prototype early-type galaxy sub-classes. 
In the flux decompositions, the spheroid (or bulge) and the disc are shown with the red and blue color, respectively. 
The left panel shows a lenticular galaxy, composed of a bulge encased in a large-scale disc. 
The right panel displays an elliptical galaxy with (an optional) nuclear stellar disc. 
The middle panel presents an early-type galaxy with an intermediate-sized disc embedded in the spheroid. 
We refer to the last case as an ellicular galaxy.}
\label{fig:model}
\end{center}
\end{figure}

@@

\subsection{NGC 3115}
The presence of a disc in NGC 3115 is obvious due to its edge-on orientation (Figure \ref{fig:n3115}). 
Less obvious is the radial extent of this disc, if one only relies on a visual inspection of the galaxy image. 
The ellipticity profile (Figure \ref{fig:n3115}) is consistent with the presence of an intermediate-scale disc. 
Moreover, the kinematics of NGC 3115 \citep{arnold2011n3115} also disprove the presence of a large-scale disc, 
because the galaxy is rapidly rotating only within two galaxy half-light radii ($\sim 2 \times 50~\rm arcsec$), 
and the rotation significantly drops at larger radii.  
The unsharp mask of NGC 3115 (Figure \ref{fig:n3115}) betrays the presence of a faint edge-on nuclear ring, 
which can also be spotted as a small peak in the ellipticity profile 
(at semi-major axis length $R_{\rm maj} \sim 15~\rm arcsec$). 
Such rings are common in early-type galaxies \citep{michardmarchal1993}.
The spheroidal component of NGC 3115 is well described with a \cite{sersic1963} profile.
The highly inclined intermediate-scale disc is better fit with an $n<1$ S\'ersic profile 
(the S\'ersic index $n$ regulates the curvature of the S\'ersic profile) 
rather than with an exponential function, 
as explained by \cite{pastrav2013a}. 
The nuclear ring is modelled with a Gaussian function. \\
In comparison, \cite{lasker2014data} fit NGC 3115 with a bulge + disc + envelope, 
and measured a bulge half-light radius of $3.9~\rm arcsec$ and a bulge-to-total ratio of $0.12$. 
We describe this galaxy using a spheroid + intermediate-scale disc + nuclear ring, 
and obtain a spheroid half-light radius of $43.6~\rm arcsec$ and a spheroid-to-total ratio of $0.85$. 
We have used both kinematical information and ellipticity profiles, 
together with the surface brightness profile, 
to obtain a physically consistent and meaningful model.

\subsection{NGC 1332}
The morphology of NGC 1332 (Figure \ref{fig:n1332}) is very similar to that of NGC 3115, 
with the ellipticity profile indicating the presence of an intermediate-scale disc, 
although in this case no nuclear component is evident. 
We were not able to find any extended kinematic profile or map 
for this galaxy in the literature. 
The data within the innermost $6~\rm arcsec$ were excluded from the fit 
because, according to our galaxy decomposition, they are possibly affected by the presence of a partially depleted core.
The surface brightness profile of NGC 1332 is well described with a S\'ersic-spheroid plus
an $n<1$ S\'ersic-disc. 
Our galaxy decomposition suggests that NGC 1332 is a spheroid-dominated galaxy, 
with a spheroid-to-total ratio of $0.95$. \\
\cite{rusli2011} did not identify the restricted extent of the intermediate-scale disc, 
as revealed by the ellipticity profile, 
and proposed a model featuring a S\'ersic-bulge and a large-scale exponential-disc, 
with a spheroid-to-total ratio of $0.43$.
Based on their bulge/disc decomposition, they concluded that NGC 1332 is a disc-dominated lenticular galaxy 
which is displaced from the (black hole mass)-(spheroid luminosity) correlation of \cite{marconihunt2003} 
by an order of magnitude along the black hole mass direction. 
However, in Section \ref{sec:mm} we show that, according to our decomposition, 
NGC 1332 lies within the $1\sigma$ scatter about the (black hole mass)-(spheroid stellar mass) correlation 
for early-type galaxies. 
We also note that the majority of galaxies with an elevated stellar velocity dispersion ($\sigma > 270~\rm km~s^{-1}$) 
are core-S\'ersic galaxies \citep{graham2003coresersicmodel,ferrarese2006acsvcs,dullograham2014cores}, 
i.e.~they have a partially depleted core which has been identified from high-resolution photometric data. 
NGC 1332 has $\sigma = 320~\rm km~s^{-1}$, but, 
based on their decomposition of \emph{HST} imaging, \cite{rusli2011} did not find a core in this galaxy. 
However, our galaxy decomposition (Figure \ref{fig:n1332}) suggests that NGC 1332 is in fact a core-S\'ersic galaxy. 
Since we did not use high-resolution photometric data, 
we refrain from a firm conclusion, 
but we caution that a re-analysis of the \emph{HST} data -- by taking into account the correct radial extent of the intermediate-scale disc --
may indeed reveal the presence of a depleted core in this galaxy.

@@

\subsubsection{NGC 1271}
\cite{walsh2015} explored a three-component decomposition for NGC 1271 
and identified the galaxy bulge with the innermost of the three components, 
having a half-light radius of $0.61~\rm arcsec$ and a bulge-to-total flux ratio of $0.23$; 
our model features a spheroid + intermediate-scale disc, 
with a spheroid half-light radius of $3.3~\rm arcsec$ and a spheroid-to-total flux ratio of $0.67$.

\subsubsection{NGC 1277}
\cite{vandenbosch2012} proposed a model for the galaxy NGC 1277 with a bulge + disc + nuclear source + envelope, 
which gives a bulge half-light radius of $0.9~\rm arcsec$ and a bulge-to-total flux ratio of $0.24$; 
our model consists of a spheroid + intermediate-scale disc + nuclear component, 
and produces a spheroid half-light radius of $6.0~\rm arcsec$ and a spheroid-to-total flux ratio of $0.79$.

\subsubsection{NGC 3377}
\cite{lasker2014data} modelled the galaxy NGC 3377 with a bulge + nuclear disc + disc + envelope, 
and obtained a bulge half-light radius of $10.1~\rm arcsec$ and a bulge-to-total flux ratio of $0.35$; 
our model with a spheroid + intermediate-scale disc + nuclear disc 
returns a spheroid half-light radius of $61.8~\rm arcsec$ and a spheroid-to-total flux ratio of $0.94$.

\subsubsection{NGC 821}
\cite{lasker2014data} decomposed the galaxy NGC 821 into a bulge + disc + envelope, 
and measured a bulge half-light radius of $3.8~\rm arcsec$ and a bulge-to-total flux ratio of $0.19$; 
our decomposition consists of a spheroid + intermediate-scale disc, 
with a spheroid half-light radius of $36.5~\rm arcsec$ and a spheroid-to-total flux ratio of $0.79$.

\subsubsection{NGC 4697}
The galaxy NGC 4697 represents an ``extreme'' case. 
\cite{lasker2014data} fit this galaxy with a bulge + nuclear source + disc + envelope, 
and obtained a bulge half-light radius of $6.3~\rm arcsec$ and a bulge-to-total flux ratio of $0.08$; 
we described NGC 4697 using a spheroid + intermediate-scale disc + nuclear disc model, 
and measured a spheroid half-light radius of $239.3~\rm arcsec$ and a spheroid-to-total flux ratio of $0.89$. \\

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{n3115_image.jpeg}
\includegraphics[width=0.49\columnwidth]{n3115_unsharp.jpeg} \\
\includegraphics[width=1.05\columnwidth]{n3115_decomposition.pdf}
\caption{NGC 3115. 
The top panels are the \emph{Spitzer}/IRAC $3.6~\rm \mu m$ image (left) and its unsharp mask (right), 
obtained by dividing the image by a Gaussian-smoothed version of itself. 
The bottom plots display the best-fit model of the surface brightness profile, $\mu$, 
and the ellipticity profile, $\epsilon$, 
along the major-axis, $R_{\rm maj}$. 
The black points are the observed data, which extend out to five galaxy half-light radii ($\sim 5 \times 50~\rm arcsec$). 
The color lines represent the individual (PSF-convolved) model components: 
red = S\'ersic (spheroid), blue = S\'ersic (disc), gray = Gaussian ring. 
The residual profile (data $-$ model) is shown as $\Delta \mu$. 
The horizontal gray dashed line corresponds to an intensity equal to three times the root mean square of the sky background fluctuations. 
$\Delta$ denotes the root mean square scatter of the fit in units of $\rm mag~arcsec^{-2}$. }
\label{fig:n3115}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{n1332_image}
\includegraphics[width=0.49\columnwidth]{n1332_unsharp} \\
\includegraphics[width=1.03\columnwidth]{n1332_decomposition.pdf}
\caption{NGC 1332.
Same as Figure \ref{fig:n3115}, except for the following. 
The surface brightness profile extends out to seven galaxy half-light radii ($\sim 7 \times 20~\rm arcsec$). 
The empty points are data excluded from the fit. 
}
\label{fig:n1332}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{mrk1216_image.jpeg}
\includegraphics[width=0.49\columnwidth]{mrk1216_unsharp.jpeg} \\
\includegraphics[width=1.05\columnwidth]{mrk1216_decomposition.pdf}
\caption{Mrk 1216. 
Same as Figure \ref{fig:n3115}, except for the following. 
The top panels are the \emph{HST}/WFC3 \emph{F160W} image (left) and its unsharp mask (right).
The surface brightness profile extends out to five galaxy half-light radii ($\sim 5 \times 5~\rm arcsec$). 
The color lines represent the individual (PSF-convolved) model components:
red = S\'ersic (spheroid), blue = exponential (disc).
}
\label{fig:m1216}
\end{center}
\end{figure}

@@

but almost constant mass-to-light ratios ($\sim$$0.6$, \citealt{meidt2014}). \\

@@

@@
